Plant-pollintor networks worldwide are composed by the same specific building

### 2021-08-06 Draft/Draft.Rmd
Some minor edits

We have compiled 60 plant-pollinator networks from 18 different studies (Table S1). All studies sampled plant-pollinator interactions in natural systems and were selected based on wide geographical coverage and the presence of interaction frequency as a measure of interaction strength. In total, there were 503 plant species, 1,111 pollinator species and 6248 of pairwise interactions registered. For ease of data manipulation plant and pollinator species names were standardize with the help of the package _taxize_ version 0.9.99 [@chamberlain2020].

@@

First, plant species were grouped into the optimal number of functional groups that summarized the main plant reproductive strategies. This was done with the help of hierarchical cluster analysis by using the trait dataset collated in Lanuza et al., (unpublished) that comprised 1,506 plant species and contained the same 60 plant-pollinator networks used in this study plus some non-weighted and weighted metawebs (see Table S1 Lanuza et al., unpublished). This dataset consisted on 8 floral, 4 reproductive and 3 vegetative traits (Table S2). We opted to calculate the plant functional groups on this larger set of species because of the higher accuracy when delimiting the functional groups with that many variables @dolnicar2014. For this, we calculated the distance of the different functional traits with the function _gowdis_ from the package _FD_ version 1.0-12 [@laliberte2014] with the method ward.D2 used for non-squared distances [@murtagh2014]. All the numerical traits were previously scaled. Finally, we applied a hierarchical cluster analysis with the function _hclust_ from the _R_ stats package version 4.0.5 and calculated the optimal number of clusters with the function _kgs_ from the package _maptree_ version 1.4-7 [@white2009].

Second, pollinators were grouped into functional groups based on taxonomic rank. We opted to divide pollinators on the taxonomic rank level and not with functional traits because (i) the main taxonomic orders differ in form and behaviour and (ii) the lower complexity of higher taxonomic ranks (i.e., pollinators had 6 orders versus plants that had 38). Hence, we grouped pollinators into 6 functional groups: (i) Hymenoptera-Anthophila (bees), (ii) Hymenoptera-non-Anthophila (other non-bee Hymenoptera), (iii) Syrphidae-Diptera, (iv) non-Syrphidae-Diptera, (v) Lepidoptera and (vi) Coleoptera.

@@

We calculated the frequency of all motifs up to five nodes (see Figure 1) for each empirical network, by using the _bmotif_ package [@bmotifsimmons2019]. To control for variation in network size and for the fact that smaller motifs can be nested within larger motifs, the frequencies were normalised as a proportion of the total number of motifs within each motif class (i.e., the number of nodes a motif contains). Like [@simmons2020], we just used five-node motifs in our analyses for visualisation, interpretation and computational reasons. In addition, we also excluded two-node motifs (or links) from our analyses because their normalised frequencies would always equal one.

>>>>

We have compiled 60 plant-pollinator networks from 18 different studies (Table S1). All studies sampled plant-pollinator interactions in natural systems and were selected based on wide geographical coverage and the presence of interaction frequency as a measure of interaction strength. In total, there were 503 plant species, 1,111 floral visitors species and 6248 of pairwise interactions registered. For ease of data manipulation plant and floral visitors species names were standardize with the help of the package _taxize_ version 0.9.99 [@chamberlain2020].

@@

First, plant species were grouped into the optimal number of functional groups that summarized the main plant reproductive strategies. This was done with the help of hierarchical cluster analysis by using the trait dataset collated in Lanuza et al., (unpublished) that comprised 1,506 plant species and contained the same 60 plant-pollinator networks used in this study plus some non-weighted and weighted metawebs (see Table S1 Lanuza et al., unpublished). This dataset consisted on 8 floral, 4 reproductive and 3 vegetative traits (Table S2). We opted to calculate the plant functional groups on this larger set of species because of the higher accuracy when delimiting the functional groups with that many variables @dolnicar2014. For this, we calculated the distance of the different functional traits with the function _gowdis_ from the package _FD_ version 1.0-12 [@laliberte2014] with the method _ward.D2_ used for non-squared distances [@murtagh2014]. All numerical traits were previously scaled. Finally, we applied a hierarchical cluster analysis with the function _hclust_ from the _R_ stats package version 4.0.5 and calculated the optimal number of clusters with the function _kgs_ from the package _maptree_ version 1.4-7 [@white2009].

Second, floral visitors were grouped into functional groups based on taxonomic rank. We opted to divide floral visitors on the taxonomic rank level and not with functional traits because (i) the main taxonomic orders differ in form and behaviour and (ii) the lower complexity of higher taxonomic ranks (i.e., floral visitors had 6 orders versus plants that had 38). Hence, we grouped floral visitors into 6 functional groups that represented the main life strategies: (i) Hymenoptera-Anthophila (bees), (ii) Hymenoptera-non-Anthophila (other non-bee Hymenoptera), (iii) Syrphidae-Diptera, (iv) non-Syrphidae-Diptera, (v) Lepidoptera and (vi) Coleoptera.

@@

We calculated the frequency of all motifs up to five nodes (see Figure 1) for each empirical network, by using the _bmotif_ package [@bmotifsimmons2019]. To control for variation in network size, motif frequencies were normalised as a proportion of the total number of motifs within each motif class (i.e., the number of nodes a motif contains). Like @simmons2020, we just used five-node motifs in our analyses for visualisation, interpretation and computational reasons. In addition, we also excluded two-node motifs (or links) from our analyses because their normalised frequencies would always equal one.
